### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@43d0f0111ac6b747baa7fd465a604a6ff369e8a3 🚀

\hypertarget{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}{%
\section{The metaweb embeds hypotheses about which spatial boundaries
are
meaningful}\label{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}}

>>>>

\hypertarget{the-metaweb-embeds-strong-ecological-hypotheses}{%
\section{The metaweb embeds strong ecological
hypotheses}\label{the-metaweb-embeds-strong-ecological-hypotheses}}
